A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-28 paper/paper.Rnw
Finish text for heatmaps

We have proposed several hypotheses to explain why the model's predictions are not entirely consistent with manual labels on the images. We can test these hypotheses by examining what the model ``sees" when making its predictions. Heatmaps, also known as Class Activation Maps (CAMs), are a visual diagnostic tool that highlights the areas of an image that are most significant to classification for a given class \citep{chollet_allaire_2018}. Using these graphics, we can identify which locations in an image contribute most to the model's predictions. \mt{Figures \ref{fig:ugg-heatmap}-\ref{fig:dc-heatmap} show a number of images alongside heatmaps for the four classes with the highest output probabilities for each image. These heatmaps can confirm that a number of misclassifications are a result of overlapping features between classes, and that the model is using reasonable features to make predictions.}

\mt{The captions are pretty detailed. Do I have to say more?} %\autoref{fig:ugg-heatmap} shows predictions and heatmaps for the logo from an UGG shoe. The model correctly identifies triangles and text, and references appropriate regions of the image. The model identifies a circle as well; while it could be argued that the triangles form an implicit circle, the heatmap demonstrates that the circular portion of the image is the 'G', which would not be a closed figure labeled as a circle. The model's prediction of the presence of a circle is understandable, but incorrect. In \autoref{fig:seychelles-heatmap}, the model assigns high probabilities to text and circle. The prediction of text is correct, but the prediction of circle is not---there are very round shapes, but they do not form a closed figure that could be identified as a circle. \autoref{fig:dc-heatmap} shows a DC shoe with repeating instances of a shape that is a combination of a circle and quadrilateral, but does not technically fall into either of those categories by our definition. The model assigns high probabilities of circle and quadrilateral and indicates that the proper image features are being used for this classification. The prediction of polygon is incorrect but reasonable considering that many small hexagons are indistinguishable from circles.

% \fix{Choose three (or four) heatmaps:
% \begin{itemize}
% \item An image with multiple true shapes that the model clearly predicts well, to prove that it has learned the features we think it should (probably an UGG logo)
% \item (Seychelles circle/text confusion)
% \item \sout{An image with high quad/tri/poly confusion, but the model uses appropriate features to make educated guesses}
% \item An image with no true classes but would yield false positives (e.g., corks, puzzle pieces) to show that there will always be weird shapes that our classification can't be expected to cover, but our model will still behave reasonably enough when encountering these cases.
% \end{itemize}}

>>>>

We have proposed several hypotheses to explain why the model's predictions are not entirely consistent with manual labels on the images. We can test these hypotheses by examining what the model ``sees" when making its predictions. Heatmaps, also known as Class Activation Maps (CAMs), are a visual diagnostic tool that highlights the areas of an image that are most significant to classification for a given class \citep{chollet_allaire_2018}. Using these graphics, we can identify which locations in an image contribute most to the model's predictions.

\mt{Figures \ref{fig:ugg-heatmap}-\ref{fig:dc-heatmap} show a number of images alongside heatmaps for the four classes with the highest output probabilities for each image. \autoref{fig:ugg-heatmap} shows predictions and heatmaps for the logo from an UGG shoe. The model correctly identifies triangles and text, and references appropriate regions of the image. The prediction of a circle is shown to be associated with the letter 'G'; although this prediction is technically incorrect, it indicates that the model has learned to associate curved shapes with circles. This association is again seen in the high predicted probability of circle in \autoref{fig:seychelles-heatmap}. In this case, the prediction of text is again correct,, but the prediction of circle is not---there are very round shapes, but they do not form a closed figure that could be identified as a circle. \autoref{fig:dc-heatmap} shows a DC shoe with repeating instances of a shape that is a combination of a circle and quadrilateral, but does not technically fall into either of those categories by our definition. The model assigns high probabilities of circle and quadrilateral and indicates that the proper image features are being used for this classification. Additionally, the prediction of polygon is incorrect but reasonable considering that many small hexagons are indistinguishable from circles. These heatmaps can confirm that a number of misclassifications are a result of overlapping features between classes, and that the model is using reasonable features to make predictions.}
